Factor Analysis on Report Citations, using a Combined Latent and logistic Model

### 2019-07-19 Manuscript for submission/manuscript.tex
Update

\begin{theorem} \label{Th:th1}
Under the assumptions \ref{Ass:1} and \ref{Ass:2},
if we solve the convex problem (\ref{eq:1}) with a pair of regularization parameter $(\delta,\gamma)$ satisfying 
\begin{align}
\delta \geq 2\|\frac{1}{n}(X-P^{*})\|_{op} \quad and \quad \gamma \geq 2\|\frac{1}{n}(X-P^{*})\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg)
\end{align}
There exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$ and $s = 1,2,...,n^{2}$, we have following upper bound on $e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$
\begin{align}
    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \leq
    \underbrace{c_{1}\frac{\delta^{2}}{\tau^{2}}}
    _{\mathcal{K}_{\alpha^*}} +
    \underbrace{c_{2}\frac{\delta^{2}}{\tau^{2}}
    \bigg\{k + \frac{\tau}{\delta}\sum_{j=k+1}^{n}\sigma_{j}(L^{*})\bigg\}}_{\mathcal{K}_{L^*}} +
    \underbrace{c_{3}\frac{\gamma^{2}}{\tau^{2}}
    \bigg\{s + \frac{\tau}{\gamma}\sum_{(i,j) \notin \mathbb{M}}|S^*_{ij}|\bigg\}}_{\mathcal{K}_{S^*}}
\end{align}
where $\mathbb{M}$ is an arbitrary subset of matrix indices of cardinality at most s.
\end{theorem}

Our result provides the upper-bound on non-asymptotic Frobenius norm between estimator $\hat{\alpha}\mathbbm{1}\mathbbm{1}^T$, $\widehat{L}$ and $\widehat{S}$, and ground truth $\alpha^*\mathbbm{1}\mathbbm{1}^T$, $L^*$ and $S^*$, where matrices $L^*$ that can be either approximately or exactly low rank, and matrices $S^*$ that also can be either approximately or exactly sparse. 
A close observation on terms in upper-bound reveals that error bounds associated with $\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2}$, $\|\widehat{\Delta}^{L}\|_{F}^{2}$, and $\|\widehat{\Delta}^{S}\|_{F}^{2}$ are represented in the form of $\mathcal{K}_{\alpha^*}$, $\mathcal{K}_{L^*}$, and $\mathcal{K}_{S^*}$ respectively.
More specifically, terms $\mathcal{K}_{L^*}$ and $\mathcal{K}_{S^*}$ are comprised of two types of errors, \emph{Estimation error} and \emph{Approximation error}. ''\emph{Estimation error}'' represents statistical cost of estimating a parameter belong to the model subspace $\mathbb{M}$

This result helps us to understand the behavior of our proposed estimator both in practice and in ideal cases.
In real-world, large scale citation network analysis, it is difficult to expect exactly $k(\ll n)$ number of topics embedded in network. There must be

Specifically, when $L^*$ is an exact low rank matrix with rank $k$ (i.e., $rank(L^*)=k$) and $S^*$ is a sparse matrix, which lies within model subspace $\mathbb{M}$ (i.e., $|supp(S^*)|=s$), then we have Frobenius error bound as follows:
\[
    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \lesssim (\delta^2+1)k+\gamma^2s
\]

\emph{\textbf{Comparison to Agarwal et al, \cite{agarwal2012noisy}}}
We would like to refer readers that result presented in \textbf{Theorem \ref{Th:th1}} is similar with that of Theorem 1 presented in paper \cite{agarwal2012noisy}. 
However, it should be noted that the convex program we consider is distinct from \cite{agarwal2012noisy}.
\cite{agarwal2012noisy} considers matrix decomposition problem, where the observations are noisy realization of linear transformation $\Xi$ of the sum of (approximately) low rank and (approximately) sparse matrices. 
They used the notions of Restricted Strong Convexity of quadratic loss function and decomposable regularizer to prove their claims. In our work, we consider a convex problem, whose logistic loss 
For the completeness of paper, we provide the proof of theorem in appendix section.

\section{Appendix}
\begin{proof}
Since $\widehat{\Theta}$ and $\Theta^{*}$ are optimal and feasible (respectively) for the convex program (\ref{eq:1}), we have
\begin{equation}\label{eq:2}
    h(\widehat{\Theta}) + \delta\|\widehat{L}\|_{*} + \gamma\|\widehat{S}\|_{1} \leq  
     h(\Theta^{*}) + \delta\|{L^{*}}\|_{*} + \gamma\|{S}^{*}\|_{1}
\end{equation}

@@

Further, by plugging in Lemma 1 to get an upper bound on  $\mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})$, we can rewrite the above inequality as follows:
\begin{align}
    \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} -
    \frac{\delta}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} 
    \leq 
    \frac{7\delta}{2}\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) + 4 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 4\gamma \|S^*_{M^\perp}\|_{1}  \label{eq:42}
\end{align}
Noting that $\widehat{\Delta}^{L}_{A}$ has rank at most 2$k$ and that $\widehat{\Delta}^{S}_{M}$ lies in the model space $\mathbb{M}$, we find that
\begin{align}
    \nonumber 
    \delta\mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) 
    \leq \sqrt{2k}\delta\|\widehat{\Delta}^L_{A}\|_{F} + \Psi(\mathbb{M})\gamma\|\widehat{\Delta}^S_\mathbb{M}\|_{F}\\
    \leq \sqrt{2k}\delta\|\widehat{\Delta}^L\|_{F} + \Psi(\mathbb{M})\gamma\|\widehat{\Delta}^S\|_{F}  \label{eq:43}
\end{align}
Here $\Psi(\mathbb{M})$ measures the compatibility between Frobenius norm and component-wise $\ell_{1}$ regularizer, where $\mathbb{M}$ is an arbitrary subset of matrix indices of cardinality at most s. 
\[
    \Psi(\mathbb{M}):=\sup\limits_{U\in\mathbb{M},U\neq0}\frac{\|U\|_{1}}{\|U\|_{F}}
\]
Using Cauchy-Schwarz inequality, we can easily check the quantity $\Psi(\mathbb{M})$ is bounded by at most $\sqrt{s}$. Plugging in the relation ($\ref{eq:43}$) into ($\ref{eq:42}$) and rearranging the term relevant with  $e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$ yield the claim.
\end{proof}

\subsection{Proof of Lemma 1}
\begin{proof}
Through the application of basic inequality by using optimality of $\widehat{\Theta}$ and feasibility of $\Theta^{*}$ to convex program (\ref{eq:1}), we have
\begin{equation}
    h(\widehat{\Theta}) - h(\Theta^{*})
    \leq \delta \mathbb{Q}(L^{*},S^{*}) - \delta \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})
\end{equation}
By using convexity of $h(\Theta)$, we can write
\begin{align}
    h(\widehat{\Theta})-h(\Theta^{*}) &\geq 
    \langle\, \nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\ \nonumber \\
    &= - \langle\,\frac{1}{n} (X-P^{*}), \hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T + \widehat{\Delta}^{L} + \widehat{\Delta}^{S} \rangle\ \nonumber \\
    &\geq -\frac{1}{n} \|X - P^*\|_{op}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_\ast + \|\widehat{\Delta}^{L}\|_\ast) +  \frac{1}{n} \|X - P^*\|_{\infty}\|\widehat{\Delta}^{S}\|_{1} \nonumber \\ 
    &\geq -\frac{\delta}{2}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_F + \|\widehat{\Delta}^{L}_{A}\|_\ast + \|\widehat{\Delta}^{L}_{B}\|_\ast) - \frac{\delta}{2} (\|\widehat{\Delta}^{S}_{\mathbb{M}}\|_{1} + 
    \|\widehat{\Delta}^{S}_{\mathbb{M^\perp}}\|_{1}) \label{eq:27}
\end{align}

>>>>

\begin{theorem} \label{Th:th1}
Under the assumptions \ref{Ass:1} and \ref{Ass:2},
if we solve the convex problem (\ref{eq:1}) with a pair of regularization parameter $(\delta,\gamma)$ satisfying 
\begin{align} \label{eq:49}
\delta \geq 2\|\frac{1}{n}(X-P^{*})\|_{op} \quad and \quad \gamma \geq 2\|\frac{1}{n}(X-P^{*})\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg)
\end{align}
There exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$ and $s = 1,2,...,n^{2}$, we have following upper bound on $e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$
\begin{align}
    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \leq
    \underbrace{c_{1}\frac{\delta^{2}}{\tau^{2}}}
    _{\mathcal{K}_{\alpha^*}} +
    \underbrace{c_{2}\frac{\delta^{2}}{\tau^{2}}
    \bigg\{k + \frac{\tau}{\delta}\sum_{j=k+1}^{n}\sigma_{j}(L^{*})\bigg\}}_{\mathcal{K}_{L^*}} +
    \underbrace{c_{3}\frac{\gamma^{2}}{\tau^{2}}
    \bigg\{s + \frac{\tau}{\gamma}\sum_{(i,j) \notin \mathbb{M}}|S^*_{ij}|\bigg\}}_{\mathcal{K}_{S^*}}
\end{align}
where $\mathbb{M}$ is an arbitrary subset of matrix indices of cardinality at most s.
\end{theorem}

We would first like to note readers that the result presented in \textbf{Theorem \ref{Th:th1}} can be thought of as an extension of Theorem 1 presented in paper \cite{agarwal2012noisy} to generalized linear model. 
Our work considers a logistic loss function whose parameters are characterized by sparse plus low rank matrices, whereas \cite{agarwal2012noisy} works on quadratic loss of noisy realization of linear transformation of sum of low rank and sparse matrices. 
We show that similar proof techniques can be applied in our case, giving us similar results.
%Detailed descriptions of each terms in bound are elaborated in paper \cite{agarwal2012noisy}.

Result of Theorem provides a family of upper-bounds, one for each indexed by a specific choice of model subspace $\mathbb{M}$, and rank parameter $k$. This family of upper-bounds helps us to understand the behavior of our proposed estimator both in practice and in ideal cases. In real-world, large scale citation network analysis, it is difficult to expect network with $L^*$ matrix with exactly $k(\ll n)$ non-zero eigenvalues, but with a matrix $L^*$ with approximately low rank.
In this case, our theorem provides the intuition on the rate on how fast the error bound $\mathcal{K}_{L^*}$ will grow.  
In ideal cases where $L^*$ is an exact low rank matrix with rank $k$ (i.e., $rank(L^*)=k$) and $S^*$ is a sparse matrix, which lies within model subspace $\mathbb{M}$ (i.e., $|supp(S^*)|=s$), we can easily verify ``\emph{approximation error}'' terms in $\mathcal{K}_{L^*}$ (i.e., $\tau\sum_{j=k+1}^{n}\sigma_j(L^*)$) and in $\mathcal{K}_{S^*}$ (i.e., $\tau\sum_{(i,j)\notin \mathbb{M}}|S_{ij}^*|$) disappear, giving us Frobenius error bound as follows:
\[
    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \lesssim \delta^2(k+1)+\gamma^2s
\]
where $\lesssim$ denotes that we ignore constant factors.

\section{Appendix}
\subsection{Proof of Theorem \ref{Th:th1}}

In proof, we use the notion of \emph{decomposable regularizer} which is studied at length in the work \cite{negahban2012unified}. Let $(\mathbb{M},\mathbb{M}^{\perp})$ denote arbitrary subspace pair for which component-wise $\ell_{1}$ norm is decomposable. Throughout the proof, we adopt the convenient short-hand notation on projection of matrix $P$ on subspace $\mathbb{M}$ as $P_{\mathbb{M}}$. And also note that proof relies on following lemma:

\begin{lemma} \label{le:le1}
If a pair of regularization parameters $(\delta,\gamma)$ satisfies condition (\ref{eq:49}), then for $\mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})$, we have
\[
    \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}) \leq 
    \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} + 
    3\mathbb{Q}(\widehat{\Delta}^{L}_{A},\widehat{\Delta}^{S}_{M})+4 \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 4\frac{\gamma}{\delta}   
    \|S^{*}_{M^\perp}\|_{1}
\]
\end{lemma}

\noindent\textbf{proof of Theorem \ref{Th:th1}}
\begin{proof}
Since $\widehat{\Theta}$ and $\Theta^{*}$ are optimal and feasible (respectively) for the convex program (\ref{eq:1}), we have
\begin{equation}\label{eq:2}
    h(\widehat{\Theta}) + \delta\|\widehat{L}\|_{*} + \gamma\|\widehat{S}\|_{1} \leq  
     h(\Theta^{*}) + \delta\|{L^{*}}\|_{*} + \gamma\|{S}^{*}\|_{1}
\end{equation}

@@

Further, by plugging in Lemma \ref{le:le1} to get an upper bound on  $\mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp})$, we can rewrite the above inequality as follows:
\begin{align}
    \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\widehat{\Delta}^{S}\|_{F}^{2} -
    \frac{\delta}{2} \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} 
    \leq 
    \frac{7\delta}{2}\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) + 4 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 4\gamma \|S^*_{M^\perp}\|_{1}  \label{eq:42}
\end{align}
Noting that $\widehat{\Delta}^{L}_{A}$ has rank at most 2$k$ and that $\widehat{\Delta}^{S}_{M}$ lies in the model space $\mathbb{M}$, we find that
\begin{align}
    \nonumber 
    \delta\mathbb{Q}(\widehat{\Delta}^L_{A},\widehat{\Delta}^S_{M}) 
    \leq \sqrt{2k}\delta\|\widehat{\Delta}^L_{A}\|_{F} + \Psi(\mathbb{M})\gamma\|\widehat{\Delta}^S_\mathbb{M}\|_{F}\\
    \leq \sqrt{2k}\delta\|\widehat{\Delta}^L\|_{F} + \Psi(\mathbb{M})\gamma\|\widehat{\Delta}^S\|_{F}  \label{eq:43}
\end{align}
Here $\Psi(\mathbb{M})$ measures the compatibility between Frobenius norm and component-wise $\ell_{1}$ regularizer, where $\mathbb{M}$ is an arbitrary subset of matrix indices of cardinality at most s. 
\[
    \Psi(\mathbb{M}):=\sup\limits_{U\in\mathbb{M},U\neq0}\frac{\|U\|_{1}}{\|U\|_{F}}
\]
Using Cauchy-Schwarz inequality, we can easily check the quantity $\Psi(\mathbb{M})$ is bounded by at most $\sqrt{s}$. Plugging in the relation ($\ref{eq:43}$) into ($\ref{eq:42}$) and rearranging the term relevant with  $e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$ yield the claim.
\end{proof}

\subsection{Proof of Lemma \ref{le:le1}}

\begin{proof}
Through the application of basic inequality by using optimality of $\widehat{\Theta}$ and feasibility of $\Theta^{*}$ to convex program (\ref{eq:1}), we have
\begin{equation}
    h(\widehat{\Theta}) - h(\Theta^{*})
    \leq \delta \mathbb{Q}(L^{*},S^{*}) - \delta \mathbb{Q}(\widehat{\Delta}^L + L^{*},\widehat{\Delta}^S + S^{*})
\end{equation}
By using convexity of $h(\Theta)$, we can write
\begin{align}
    h(\widehat{\Theta})-h(\Theta^{*}) &\geq 
    \langle\, \nabla_{\Theta}h(\Theta^{*}),\widehat{\Theta}-\Theta^{*}\rangle\ \nonumber \\
    &= - \langle\,\frac{1}{n} (X-P^{*}), \hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T + \widehat{\Delta}^{L} + \widehat{\Delta}^{S} \rangle\ \nonumber \\
    &\geq -\frac{1}{n} \|X - P^*\|_{op}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_\ast + \|\widehat{\Delta}^{L}\|_\ast) +  \frac{1}{n} \|X - P^*\|_{\infty}\|\widehat{\Delta}^{S}\|_{1} \nonumber \\ 
    &\geq -\frac{\delta}{2}(\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_F + \|\widehat{\Delta}^{L}_{A}\|_\ast + \|\widehat{\Delta}^{L}_{B}\|_\ast) - \frac{\delta}{2} (\|\widehat{\Delta}^{S}_{\mathbb{M}}\|_{1} + 
    \|\widehat{\Delta}^{S}_{\mathbb{M^\perp}}\|_{1}) \label{eq:27}
\end{align}
